\section{Terms and Conditions}

\subsubsection{Introduction}

This page sets out the terms on which ENTITYDESCRIPTION (``we'', ``us'',
``our'') contracts with you for permission to use the {name of website}
web site and any services supplied through it (``this site''). By using
this site you agree to be bound by these terms.

In these terms and conditions the following terms are defined as
follows:

\begin{description}
\item[intellectual property]
means any rights in patents, registered and unregistered designs,
copyright, databases, trade marks, confidential information and all
other forms of intellectual property wherever in the world enforceable.
\end{description}

The nature of this contract is purely permissive. We permit you to use
this site as and when then are available. We do not contract to make
them available now or at any time or to provide any particular level of
service.

\subsubsection{Changes to Terms and Conditions}

As the nature of what we do changes, and as the regulation of the
internet evolves, we may need to amend these terms and conditions from
time to time by displaying a notice on this page indicating what will be
changed (or linking to a separate page where that information will be
available) and the date on which the new terms will come into force. We
will always give at least 7 days' notice of any variation and any
variation will be binding on you on the first occasion when you use this
site after the new terms have come into force.

\subsubsection{Use}

You agree that, in using this site, you will not interfere with the
legal rights of any other person or contravene any laws prevailing in
any of (i) the jurisdiction(s) to which you are subject; and (ii)
England and Wales. Prohibited behavour includes (but is not limited to)
any of the following:

\begin{enumerate}
\item
  infringing the intellectual property rights of any person
\item
  committing any criminal act
\item
  invading any individual's privacy
\item
  defaming any person
\item
  behaviour amounting to unlawful harassment
\item
  any form of denial of service attack
\item
  any other actionable wrong
\item
  impersonate any other person, and in particular any other participant
  of this site or any public figure
\end{enumerate}

In order to protect you, our other participants and yourselves, we have
developed a standard of conduct that is strictly enforced. You agree to
abide by that standard of conduct which requires that you abide by the
following rules concerning the use of this site:

\begin{enumerate}

\item
  You may not use this site for advertising or marketing of any kind
  (which includes non-profit organisations) without our permission
\item
  Only natural, human, persons may use this site. You are forbidden to
  use cause or allow any automated system to make use of the services
  available on this site except that we do permit the crawling of this
  site by the robots of web search engines.
\item
  No profanities or obscenities of any kind are permitted, whether as
  part of messages sent through or included in postings to forums on
  this site. This applies to profanities or obscenities disguised for
  example with asterisks. If you feel strongly about something, find
  another way to say it.
\item
  You may not use this site to transmit pornographic, lewd, obscene,
  violent, threatening or insulting material or to transmit links to any
  material of that kind.
\item
  Do not make personal attacks on other participants. Try to be civil
  even to those with whom you disagree.
\end{enumerate}

You agree to indemnify us against all loss or damage arising out of any
deliberate commission, by you, of any of the prohibited acts listed
above, or any deliberate breach of the standard of conduct already
described.

If you wish to complain about any misuse of our site please contact
\href{}{{abuse@example.com}}.

\subsubsection{Disclaimers}

Our services are provided ``as is'' and you make use of these services
at your own risk. It would be very foolish of you to rely on our service
in a way that could cause you any loss or damage. Do not do so. In
particular you should be aware of the following disclaimers:

\begin{enumerate}

\item
  While we make all reasonable efforts to ensure that our services are
  continuously available, service interruptions for reasons beyond our
  control are inevitable. \emph{We will accept no liability for any loss
  you suffer as a result of any interruption to or unavailability or
  suspension of our services however caused}.
\item
  Similarly, it is virtually impossible to eliminate all bugs from
  software, however well written. For this reason it is inevitable that
  our system will occasionally fail to work as expected even if it gives
  every sign of having done so. \emph{We therefore accept no liability
  for any loss you may suffer as a result of any failure by the site to
  perform or to have performed in the manner expected of it}. You should
  not rely on the site having worked --- for example that it has
  successfully sent an email ---. If you need that level of reliability
  you should investigate a commercial service.
\item
  Information posted by users to the site --- for example in forums or
  as comments --- is beyond our control and we accept no liability for
  it whatsoever. Even though we make reasonable efforts to ensure that
  information that we put on the site is accurate, we draw much of our
  material from third parties and cannot guarantee its accuracy. You
  therefore agree that \emph{we are not liable for any errors in
  information we supply on the site.}
\item
  It should go without saying that you take responsibility for anything
  that you write on the site, or the content of any emails that you send
  using it. While may provide templated information to assit you in
  writing an email, you should always check that you are happy for it to
  be sent under your name. Any information you contribute to the site
  will be visible to the entire world, and any email you send through it
  may be published by its recipient. People's reputations have suffered
  because of poorly thought out emails and contributions to web sites.
  Only you can make sure that doesn't happen to you. You agree that
  \emph{we are not responsible for the contents of any email you send,
  or any material you cause to be displayed on the site.}
\end{enumerate}

In no event shall we be liable for any direct, indirect, incidental,
special, exemplary or consequential damages however caused and arising
in anyway out of the use of our services or software.

\subsubsection{Privacy}

You consent to our storing and processing the personal information that
you have supplied about yourself in accordance with our Privacy Policy.

\subsubsection{Suspension and Termination}

Either party may terminate this contract at any time by giving written
notice to the other. No reason need be given for termination.

We reserve the right to do any of the following without being required
to give you any reason or notice:

\begin{enumerate}

\item
  suspend or terminate your access to all or any part of the
  functionality of this site
\item
  block access to this site from any part of the internet or by any
  particular means
\item
  implement a repeat infringer's policy pursuant to the USC 512(i) or
  any similar provision
\end{enumerate}

\subsubsection{Intellectual Property}

All the textual contents of this site are released under the {Creative
Commons Attribution-Non-Commercial-No Derivative Works 2.0 UK: England
\& Wales
\href{http://creativecommons.org/licenses/by-nc-nd/2.0/uk/}{Licence}}.
You may not copy any images, logos or style information (including style
sheets).

You grant us a non-exclusive, worldwide, licence to use any data that
you send through or upload to this site.

\subsubsection{General}

This agreement shall be governed by and be construed in accordance with
English law. Each party also agrees, to the extent that is permissible
by law, to submit to the exclusive jurisdiction of the courts of England
and Wales.

The failure by us to exercise any right under this agreement does not
constitute a waiver of that right.

If any terms of this agreement are held to be void or contrary to law,
then they shall be severed from the remainder of the agreement, which
shall be read so far as possible without them.

The Contracts (Rights of Third Parties) Act 1999 does not apply to this
agreement.

Nothing in this agreement constitutes a Partnership between the parties.

Nothing in these terms and conditions is a restriction of liability for
death or personal injury resulting from any fault on our behalf, nor
does it lower or restrict your statutory rights.
